---
title: 'CBCL~Age+Covariates Models with Tables and Graphs'
author: "Claire Campbell; prior data cleaning by Hedyeh Admadi"
date: "Version `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    fig_caption: yes
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_rype: console
  chunk_output_type: console
---

<style type="text/css">

body, td {
   font-size: 13px;
}
code.r{
  font-size: 11px;
}
pre {
  font-size: 11px
}
</style>


# R set up

Note that the data cleaning and exploration for this analysis is in a separate file called 
"HEI-Aim2-Data-Cleaning-Exploration-0219-2021" written by Hedyeh Ahmadi.
```{r}
#Clear existing data and graphics
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
graphics.off()
invisible(gc()) #free up memory and report the memory usage.
```


```{r}
knitr::opts_chunk$set(echo = TRUE)

# To create Pdf
library(knitr)

# Importing Data
library(haven)
library(readxl)

# Table specific
library(xtable)
library(kableExtra)

# Data Cleaning and plotting
library(tidyverse)
library(dplyr)
library(plyr)
library(ggplot2)
library(scales)
library(ggeffects)

# ggplot common legend
library(ggpubr)

# Skewness library
library(e1071)

# Matrix operations
library(matrixStats)

# Mixed Models
library(lme4)
library(nlme)
library(lmerTest) # to get p-values for lmer
require (HLMdiag) # Model diagnostics

# Recoding for the whole data frame
library(naniar)

# To read the lables
library(Hmisc)

# to order the data
library(doBy)

# to re-code variables
library(rockchalk)

# for reshape
library(MASS)

# descriptive and more
library(psych)

# correlogram plot
library(corrplot)

# vif
library(car)

#glmer diagnostics
library("fitdistrplus")

#outlier analysis and R^2
library(performance)

# linearity plot of glmer
library(ggResidpanel)

# interaction plots 
library(sjPlot)

#interaction plots
library(emmeans)

# Creating stratified tables
library(arsenal)

#For zero-inflated negative binomial modeling/model checking
library(NBZIMM)
library(nlme)
library(philentropy)

#For inverse logit
library(boot)

#Plot organizing
library(gridExtra)
```

# Importing the Clean Data
```{r}
HEI_Aim2_Long <- read.csv("HEI_Aim2_Long.csv")
HEI_Aim2_Wide <- read.csv("HEI_Aim2_Wide.csv")

HEI_Aim2_Long_1KidPerFamily <- read.csv("HEI_Aim2_Long_1KidPerFamily.csv")
dim(HEI_Aim2_Long)
dim(HEI_Aim2_Wide)
dim(HEI_Aim2_Long_1KidPerFamily)


names(HEI_Aim2_Long)
names(HEI_Aim2_Wide)
names(HEI_Aim2_Long_1KidPerFamily)


# Note we are keeping all families but choosing one kid per family
length(unique(HEI_Aim2_Long$rel_family_id))
length(unique(HEI_Aim2_Long$subjectid)) # matches number of rows of wide data :)

length(unique(HEI_Aim2_Long_1KidPerFamily$rel_family_id))
length(unique(HEI_Aim2_Long_1KidPerFamily$subjectid))
```

## Copy baseline variables to all timepoints for full df
```{r}
#rename so can use later
names(HEI_Aim2_Long)[names(HEI_Aim2_Long) == 'prnt.empl.bl'] <- 'prnt.empl.b'

#create dataset for table and comparison
baseline_vars <- subset(HEI_Aim2_Long, HEI_Aim2_Long$eventname=="Baseline", select = c("subjectid", "sex", "race_ethnicity", "high.educ", "neighb_phenx_avg_p", "overall.income.b", "prnt.empl.b"))

#rename variables
names(baseline_vars)[names(baseline_vars) == 'sex'] <- 'sex.bl'
names(baseline_vars)[names(baseline_vars) == 'race_ethnicity'] <- 'race_ethnicity.bl'
names(baseline_vars)[names(baseline_vars) == 'high.educ'] <- 'high.educ.bl'
names(baseline_vars)[names(baseline_vars) == 'neighb_phenx_avg_p'] <- 'neighb_phenx_avg_p.bl'
names(baseline_vars)[names(baseline_vars) == 'overall.income.b'] <- 'overall.income.bl'
names(baseline_vars)[names(baseline_vars) == 'prnt.empl.b'] <- 'prnt.empl.bl'

#add to initial df
HEI_Aim2_Long_2 <- merge(HEI_Aim2_Long, baseline_vars, by="subjectid")
```

# Creating variables for modeling and tables

The following variables are time-invariant, will use baseline covariates since PM2.5 collected at baseline:
- reshist_addr1_pm252016aa_bl which is the Baseline PM2.5.
- reshist_addr1_no2_2016_aavg_bl which is the Baseline NO2.
- sex.bl
- race_ethnicity.bl
- high.educ.bl
- prnt.empl.bl 
- neighb_phenx_avg_p.bl
- overall.income.bl 


The following variables are time-varying:
- all CBCL outcomes
- interview_age

## Copy baseline variables to all timepoints for 1KidPerFamily
```{r}
#rename so can use later
names(HEI_Aim2_Long_1KidPerFamily)[names(HEI_Aim2_Long_1KidPerFamily) == 'prnt.empl.bl'] <- 'prnt.empl.b'

#create dataset for table and comparison
baseline_vars_1KidPerFamily <- subset(HEI_Aim2_Long_1KidPerFamily, HEI_Aim2_Long_1KidPerFamily$eventname=="Baseline", select = c("subjectid", "sex", "race_ethnicity", "high.educ", "neighb_phenx_avg_p", "overall.income.b"))

#rename variables
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'sex'] <- 'sex.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'race_ethnicity'] <- 'race_ethnicity.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'high.educ'] <- 'high.educ.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'neighb_phenx_avg_p'] <- 'neighb_phenx_avg_p.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'overall.income.b'] <- 'overall.income.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'prnt.empl.b'] <- 'prnt.empl.bl'

#add to initial df
HEI_Aim2_Long_1KidPerFamily_2 <- merge(HEI_Aim2_Long_1KidPerFamily, baseline_vars, by="subjectid")
```

## Clean 1KidPerFamily
```{r}
## Cleaning
#merge Asian into Other group b/c statistically Asian group is too small
tapply(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, 
       HEI_Aim2_Long_1KidPerFamily_2$eventname,table, useNA = "always")

HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl <- 
  ifelse(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl=="Asian","Other",
         HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl)

tapply(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, 
       HEI_Aim2_Long_1KidPerFamily_2$eventname,table, useNA = "always")

#reformat variables
HEI_Aim2_Long_1KidPerFamily_2$eventname <- 
  as.factor(HEI_Aim2_Long_1KidPerFamily_2$eventname)

HEI_Aim2_Long_1KidPerFamily_2$eventname <- 
  relevel(HEI_Aim2_Long_1KidPerFamily_2$eventname , ref="Baseline")

table(HEI_Aim2_Long_1KidPerFamily_2$eventname, useNA = "always")


HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_internal_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_internal_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_external_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_external_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_anxdep_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_anxdep_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_withdep_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_withdep_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_attention_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_attention_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_rulebreak_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_rulebreak_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_aggressive_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_aggressive_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_totprob_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_totprob_r)
HEI_Aim2_Long_1KidPerFamily_2$abcd_site <- as.factor(HEI_Aim2_Long_1KidPerFamily_2$abcd_site)
HEI_Aim2_Long_1KidPerFamily_2$subjectid <- as.factor(HEI_Aim2_Long_1KidPerFamily_2$subjectid)
HEI_Aim2_Long_1KidPerFamily_2$prnt.empl.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$prnt.empl.bl, levels = c("Employed", "Stay at Home Parent", "Unemployed", "Other"))
HEI_Aim2_Long_1KidPerFamily_2$overall.income.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$overall.income.bl, levels = c("[>=100K]", "[>=50K & <100K]", "[<50k]", "[Don't Know or Refuse]"))
HEI_Aim2_Long_1KidPerFamily_2$sex.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$sex.bl, levels = c("Male", "Female"))
HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, levels = c("White", "Hispanic", "Black", "Other"))
HEI_Aim2_Long_1KidPerFamily_2$high.educ.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$high.educ.bl, levels = c("Post Graduate Degree", "Bachelor", "Some College", "HS Diploma/GED", "< HS Diploma"))
```

## Create Final Dataset
```{r results='asis'}
#create smaller df
df <- subset(HEI_Aim2_Long_1KidPerFamily_2,select=c("subjectid","abcd_site","eventname","interview_age","reshist_addr1_pm252016aa_bl","reshist_addr1_no2_2016_aavg_bl","prnt.empl.bl","overall.income.bl","sex.bl","race_ethnicity.bl","high.educ.bl","neighb_phenx_avg_p.bl","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_anxdep_r","cbcl_scr_syn_withdep_r","cbcl_scr_syn_attention_r","cbcl_scr_syn_rulebreak_r","cbcl_scr_syn_aggressive_r","cbcl_scr_syn_internal_t","cbcl_scr_syn_external_t","cbcl_scr_syn_anxdep_t","cbcl_scr_syn_withdep_t","cbcl_scr_syn_rulebreak_t","cbcl_scr_syn_aggressive_t","cbcl_scr_syn_attention_t"))

#complete cases because needed for zinb
df_cc <- df[complete.cases(df),]

#center age at 9years-old (i.e., 108 months)
df_cc$interview_age.c9 <- df_cc$interview_age-108
#change to years
df_cc$interview_age.c9.y <- df_cc$interview_age.c9/12
#scale pm2.5 by SD
#df_cc$reshist_addr1_pm252016aa_bl.scaled <- scale(df_cc$reshist_addr1_pm252016aa_bl, center = TRUE, scale = TRUE)
#center pm2.5 to 5 (recommended by WHO)
df_cc$reshist_addr1_pm252016aa_bl.c5 <- df_cc$reshist_addr1_pm252016aa_bl-5
#center no2 to 5.33 (recommended by WHO)
df_cc$reshist_addr1_no2_2016_aavg_bl.c533 <- df_cc$reshist_addr1_no2_2016_aavg_bl-5.33

#center around mean
neighb_phenx_avg_p.bl.cm <- df_cc$neighb_phenx_avg_p.bl - mean(df_cc$neighb_phenx_avg_p.bl)

#correlation between pm2.5 and no2
cor(df_cc$reshist_addr1_pm252016aa_bl.c5[df_cc$eventname=="Baseline"], df_cc$reshist_addr1_no2_2016_aavg_bl.c533[df_cc$eventname=="Baseline"], method="pearson")
```

# CBCL + Age
```{r}
#internal
internal_zinb_r <- glmm.zinb(cbcl_scr_syn_internal_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#external
external_zinb_r <- glmm.zinb(cbcl_scr_syn_external_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#anxdep
anxdep_zinb_r <- glmm.zinb(cbcl_scr_syn_anxdep_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#withdep
withdep_zinb_r <- glmm.zinb(cbcl_scr_syn_withdep_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#attention
attention_zinb_r <- glmm.zinb(cbcl_scr_syn_attention_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#rulebreak
rulebreak_zinb_r <- glmm.zinb(cbcl_scr_syn_rulebreak_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)

#aggressive
aggressive_zinb_r <- glmm.zinb(cbcl_scr_syn_aggressive_r ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl, zi_random = ~1|abcd_site, data = df_cc)
```

# FDR Correction for count function
```{r}
#calculate fdr values
#internal
internal_fdr <- as.data.frame(summary(internal_zinb_r)$tTable[,1:2])
internal_fdr$Pvalue <- summary(internal_zinb_r)$tTable[,5]
rownames(internal_fdr) <- paste0("internal.", rownames(internal_fdr))
#external
external_fdr <- as.data.frame(summary(external_zinb_r)$tTable[,1:2])
external_fdr$Pvalue <- summary(external_zinb_r)$tTable[,5]
rownames(external_fdr) <- paste0("external.", rownames(external_fdr))
#anxdep
anxdep_fdr <- as.data.frame(summary(anxdep_zinb_r)$tTable[,1:2])
anxdep_fdr$Pvalue <- summary(anxdep_zinb_r)$tTable[,5]
rownames(anxdep_fdr) <- paste0("anxdep.", rownames(anxdep_fdr))
#withdep
withdep_fdr <- as.data.frame(summary(withdep_zinb_r)$tTable[,1:2])
withdep_fdr$Pvalue <- summary(withdep_zinb_r)$tTable[,5]
rownames(withdep_fdr) <- paste0("withdep.", rownames(withdep_fdr))
#attention
attention_fdr <- as.data.frame(summary(attention_zinb_r)$tTable[,1:2])
attention_fdr$Pvalue <- summary(attention_zinb_r)$tTable[,5]
rownames(attention_fdr) <- paste0("attention.", rownames(attention_fdr))
#rulebreak
rulebreak_fdr <- as.data.frame(summary(rulebreak_zinb_r)$tTable[,1:2])
rulebreak_fdr$Pvalue <- summary(rulebreak_zinb_r)$tTable[,5]
rownames(rulebreak_fdr) <- paste0("rulebreak.", rownames(rulebreak_fdr))
#aggressive
aggressive_fdr <- as.data.frame(summary(aggressive_zinb_r)$tTable[,1:2])
aggressive_fdr$Pvalue <- summary(aggressive_zinb_r)$tTable[,5]
rownames(aggressive_fdr) <- paste0("aggressive.", rownames(aggressive_fdr))

#all age (interview_age.c9.y)
age_fdr <- rbind(internal_fdr[c("internal.interview_age.c9.y"),],external_fdr[c("external.interview_age.c9.y"),],anxdep_fdr[c("anxdep.interview_age.c9.y"),],withdep_fdr[c("withdep.interview_age.c9.y"),],attention_fdr[c("attention.interview_age.c9.y"),],rulebreak_fdr[c("rulebreak.interview_age.c9.y"),],aggressive_fdr[c("aggressive.interview_age.c9.y"),])
age_fdr$FDR.corr <- p.adjust(age_fdr$Pvalue, method="fdr")

#write.csv(age_fdr,"all_fdr_values_only_age.csv")
```

# FDR Correction for zero-inflated function
```{r}
#calculate fdr values
#internal
internal_fdr.zi <- as.data.frame(summary(internal_zinb_r$zi.fit)$tTable[,1:2])
internal_fdr.zi$Pvalue <- summary(internal_zinb_r$zi.fit)$tTable[,5]
rownames(internal_fdr.zi) <- paste0("internal.", rownames(internal_fdr.zi))
#external
external_fdr.zi <- as.data.frame(summary(external_zinb_r$zi.fit)$tTable[,1:2])
external_fdr.zi$Pvalue <- summary(external_zinb_r$zi.fit)$tTable[,5]
rownames(external_fdr.zi) <- paste0("external.", rownames(external_fdr.zi))
#anxdep
anxdep_fdr.zi <- as.data.frame(summary(anxdep_zinb_r$zi.fit)$tTable[,1:2])
anxdep_fdr.zi$Pvalue <- summary(anxdep_zinb_r$zi.fit)$tTable[,5]
rownames(anxdep_fdr.zi) <- paste0("anxdep.", rownames(anxdep_fdr.zi))
#withdep
withdep_fdr.zi <- as.data.frame(summary(withdep_zinb_r$zi.fit)$tTable[,1:2])
withdep_fdr.zi$Pvalue <- summary(withdep_zinb_r$zi.fit)$tTable[,5]
rownames(withdep_fdr.zi) <- paste0("withdep.", rownames(withdep_fdr.zi))
#attention
attention_fdr.zi <- as.data.frame(summary(attention_zinb_r$zi.fit)$tTable[,1:2])
attention_fdr.zi$Pvalue <- summary(attention_zinb_r$zi.fit)$tTable[,5]
rownames(attention_fdr.zi) <- paste0("attention.", rownames(attention_fdr.zi))
#rulebreak
rulebreak_fdr.zi <- as.data.frame(summary(rulebreak_zinb_r$zi.fit)$tTable[,1:2])
rulebreak_fdr.zi$Pvalue <- summary(rulebreak_zinb_r$zi.fit)$tTable[,5]
rownames(rulebreak_fdr.zi) <- paste0("rulebreak.", rownames(rulebreak_fdr.zi))
#aggressive
aggressive_fdr.zi <- as.data.frame(summary(aggressive_zinb_r$zi.fit)$tTable[,1:2])
aggressive_fdr.zi$Pvalue <- summary(aggressive_zinb_r$zi.fit)$tTable[,5]
rownames(aggressive_fdr.zi) <- paste0("aggressive.", rownames(aggressive_fdr.zi))

#all age (interview_age.c9.y)
age_fdr.zi <- rbind(internal_fdr.zi[c("internal.interview_age.c9.y"),],external_fdr.zi[c("external.interview_age.c9.y"),],anxdep_fdr.zi[c("anxdep.interview_age.c9.y"),],withdep_fdr.zi[c("withdep.interview_age.c9.y"),],attention_fdr.zi[c("attention.interview_age.c9.y"),],rulebreak_fdr.zi[c("rulebreak.interview_age.c9.y"),],aggressive_fdr.zi[c("aggressive.interview_age.c9.y"),])
age_fdr.zi$FDR.corr <- p.adjust(age_fdr.zi$Pvalue, method="fdr")

#write.csv(age_fdr.zi,"all_fdr_values_age_only.zi.csv")
```

# Plot main effect of age: use method on [this site](https://stats.oarc.ucla.edu/stata/faq/how-can-i-manually-generate-the-predicted-counts-from-a-zip-or-zinb-model-based-on-the-parameter-estimates/), Example 3, to calculate values manually

## Internalizing
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
internal_prediction_main <- data.frame(CBCL=c("internal","internal"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_internal <- fixef(summary(internal_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_internal <- fixef(summary(internal_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_internal <- fixef(summary(internal_zinb_r))["(Intercept)"]
age_coef_ct_internal <- fixef(summary(internal_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
internal_prediction_main$zi_age <- (inter_coef_zi_internal + age_coef_zi_internal*internal_prediction_main$Ages)
##count
###age
internal_prediction_main$count_age <- (inter_coef_ct_internal + age_coef_ct_internal*internal_prediction_main$Ages)

#calculate predictions
internal_prediction_main$pzero_age <- exp(internal_prediction_main$zi_age) / (1+exp(internal_prediction_main$zi_age))
internal_prediction_main$pcount_age <- exp(internal_prediction_main$count_age) * (1-internal_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_internal_pzero <- ((internal_prediction_main[2,5] - internal_prediction_main[1,5]) / internal_prediction_main[1,5]) * 100
round(age9to12_internal_pzero)
#45% increase

#Plot zi model
##age
internal_main.age_zi <-
  ggplot(internal_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "45% increase", x = 1.5, y = 0.035)
```

## Externalizing
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
external_prediction_main <- data.frame(CBCL=c("external","external"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_external <- fixef(summary(external_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_external <- fixef(summary(external_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_external <- fixef(summary(external_zinb_r))["(Intercept)"]
age_coef_ct_external <- fixef(summary(external_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
external_prediction_main$zi_age <- (inter_coef_zi_external + age_coef_zi_external*external_prediction_main$Ages)
##count
###age
external_prediction_main$count_age <- (inter_coef_ct_external + age_coef_ct_external*external_prediction_main$Ages)

#calculate predictions
external_prediction_main$pzero_age <- exp(external_prediction_main$zi_age) / (1+exp(external_prediction_main$zi_age))
external_prediction_main$pcount_age <- exp(external_prediction_main$count_age) * (1-external_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_external_pzero <- ((external_prediction_main[2,5] - external_prediction_main[1,5]) / external_prediction_main[1,5]) * 100
round(age9to12_external_pzero)
#88% increase
##count
age9to12_external_pcount <- ((external_prediction_main[2,6] - external_prediction_main[1,6]) / external_prediction_main[1,6]) * 100
round(age9to12_external_pcount)
#12% decrease

#Plot zi model
##age
external_main.age_zi <-
  ggplot(external_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "88% increase", x = 1.5, y = 0.035)

#plot count model
##age
external_main.age_ct <-
  ggplot(external_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "12% decrease", x = 1.5, y = 3.3)
```

## Anxious/Depressed
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
anxdep_prediction_main <- data.frame(CBCL=c("anxdep","anxdep"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_anxdep <- fixef(summary(anxdep_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_anxdep <- fixef(summary(anxdep_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_anxdep <- fixef(summary(anxdep_zinb_r))["(Intercept)"]
age_coef_ct_anxdep <- fixef(summary(anxdep_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
anxdep_prediction_main$zi_age <- (inter_coef_zi_anxdep + age_coef_zi_anxdep*anxdep_prediction_main$Ages)
##count
###age
anxdep_prediction_main$count_age <- (inter_coef_ct_anxdep + age_coef_ct_anxdep*anxdep_prediction_main$Ages)

#calculate predictions
anxdep_prediction_main$pzero_age <- exp(anxdep_prediction_main$zi_age) / (1+exp(anxdep_prediction_main$zi_age))
anxdep_prediction_main$pcount_age <- exp(anxdep_prediction_main$count_age) * (1-anxdep_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_anxdep_pzero <- ((anxdep_prediction_main[2,5] - anxdep_prediction_main[1,5]) / anxdep_prediction_main[1,5]) * 100
round(age9to12_anxdep_pzero)
#185% increase
##count
age9to12_anxdep_pcount <- ((anxdep_prediction_main[2,6] - anxdep_prediction_main[1,6]) / anxdep_prediction_main[1,6]) * 100
round(age9to12_anxdep_pcount)
#8% decrease

#Plot zi model
##age
anxdep_main.age_zi <-
  ggplot(anxdep_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "185% increase", x = 1.5, y = 0.035)

#plot count model
##age
anxdep_main.age_ct <-
  ggplot(anxdep_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "8% decrease", x = 1.5, y = 3.3)
```

## withdepizing
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
withdep_prediction_main <- data.frame(CBCL=c("withdep","withdep"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_withdep <- fixef(summary(withdep_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_withdep <- fixef(summary(withdep_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_withdep <- fixef(summary(withdep_zinb_r))["(Intercept)"]
age_coef_ct_withdep <- fixef(summary(withdep_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
withdep_prediction_main$zi_age <- (inter_coef_zi_withdep + age_coef_zi_withdep*withdep_prediction_main$Ages)
##count
###age
withdep_prediction_main$count_age <- (inter_coef_ct_withdep + age_coef_ct_withdep*withdep_prediction_main$Ages)

#calculate predictions
withdep_prediction_main$pzero_age <- exp(withdep_prediction_main$zi_age) / (1+exp(withdep_prediction_main$zi_age))
withdep_prediction_main$pcount_age <- exp(withdep_prediction_main$count_age) * (1-withdep_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_withdep_pzero <- ((withdep_prediction_main[2,5] - withdep_prediction_main[1,5]) / withdep_prediction_main[1,5]) * 100
round(age9to12_withdep_pzero)
#45% decrease
##count
age9to12_withdep_pcount <- ((withdep_prediction_main[2,6] - withdep_prediction_main[1,6]) / withdep_prediction_main[1,6]) * 100
round(age9to12_withdep_pcount)
#34% increase

#Plot zi model
##age
withdep_main.age_zi <-
  ggplot(withdep_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "45% decrease", x = 1.5, y = 0.035)

#plot count model
##age
withdep_main.age_ct <-
  ggplot(withdep_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "34% increase", x = 1.5, y = 3.3)
```

## Attention
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
attention_prediction_main <- data.frame(CBCL=c("attention","attention"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_attention <- fixef(summary(attention_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_attention <- fixef(summary(attention_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_attention <- fixef(summary(attention_zinb_r))["(Intercept)"]
age_coef_ct_attention <- fixef(summary(attention_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
attention_prediction_main$zi_age <- (inter_coef_zi_attention + age_coef_zi_attention*attention_prediction_main$Ages)
##count
###age
attention_prediction_main$count_age <- (inter_coef_ct_attention + age_coef_ct_attention*attention_prediction_main$Ages)

#calculate predictions
attention_prediction_main$pzero_age <- exp(attention_prediction_main$zi_age) / (1+exp(attention_prediction_main$zi_age))
attention_prediction_main$pcount_age <- exp(attention_prediction_main$count_age) * (1-attention_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_attention_pzero <- ((attention_prediction_main[2,5] - attention_prediction_main[1,5]) / attention_prediction_main[1,5]) * 100
round(age9to12_attention_pzero)
#58% increase
##count
age9to12_attention_pcount <- ((attention_prediction_main[2,6] - attention_prediction_main[1,6]) / attention_prediction_main[1,6]) * 100
round(age9to12_attention_pcount)
#10% decrease

#Plot zi model
##age
attention_main.age_zi <-
  ggplot(attention_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "58% increase", x = 1.5, y = 0.035)

#plot count model
##age
attention_main.age_ct <-
  ggplot(attention_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "10% decrease", x = 1.5, y = 3.3)
```

## Rulebreak
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
rulebreak_prediction_main <- data.frame(CBCL=c("rulebreak","rulebreak"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_rulebreak <- fixef(summary(rulebreak_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_rulebreak <- fixef(summary(rulebreak_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_rulebreak <- fixef(summary(rulebreak_zinb_r))["(Intercept)"]
age_coef_ct_rulebreak <- fixef(summary(rulebreak_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
rulebreak_prediction_main$zi_age <- (inter_coef_zi_rulebreak + age_coef_zi_rulebreak*rulebreak_prediction_main$Ages)
##count
###age
rulebreak_prediction_main$count_age <- (inter_coef_ct_rulebreak + age_coef_ct_rulebreak*rulebreak_prediction_main$Ages)

#calculate predictions
rulebreak_prediction_main$pzero_age <- exp(rulebreak_prediction_main$zi_age) / (1+exp(rulebreak_prediction_main$zi_age))
rulebreak_prediction_main$pcount_age <- exp(rulebreak_prediction_main$count_age) * (1-rulebreak_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_rulebreak_pzero <- ((rulebreak_prediction_main[2,5] - rulebreak_prediction_main[1,5]) / rulebreak_prediction_main[1,5]) * 100
round(age9to12_rulebreak_pzero)
#112% increase
##count
age9to12_rulebreak_pcount <- ((rulebreak_prediction_main[2,6] - rulebreak_prediction_main[1,6]) / rulebreak_prediction_main[1,6]) * 100
round(age9to12_rulebreak_pcount)
#10% decrease

#Plot zi model
##age
rulebreak_main.age_zi <-
  ggplot(rulebreak_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "112% increase", x = 1.5, y = 0.035)

#plot count model
##age
rulebreak_main.age_ct <-
  ggplot(rulebreak_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "10% decrease", x = 1.5, y = 3.3)
```

## Aggressive
```{r}
#calculate the values at 9 and 12 years (centered at 9 yrs) at pm2.5 = 5 & 12 ug/m3 (centered at 5 ug/m3)

#df
aggressive_prediction_main <- data.frame(CBCL=c("aggressive","aggressive"), Ages=c(0,3))

#coefficients
##zi
inter_coef_zi_aggressive <- fixef(summary(aggressive_zinb_r$zi.fit))["(Intercept)"]
age_coef_zi_aggressive <- fixef(summary(aggressive_zinb_r$zi.fit))["interview_age.c9.y"]
##count
inter_coef_ct_aggressive <- fixef(summary(aggressive_zinb_r))["(Intercept)"]
age_coef_ct_aggressive <- fixef(summary(aggressive_zinb_r))["interview_age.c9.y"]

#calculate values
##zi
###age
aggressive_prediction_main$zi_age <- (inter_coef_zi_aggressive + age_coef_zi_aggressive*aggressive_prediction_main$Ages)
##count
###age
aggressive_prediction_main$count_age <- (inter_coef_ct_aggressive + age_coef_ct_aggressive*aggressive_prediction_main$Ages)

#calculate predictions
aggressive_prediction_main$pzero_age <- exp(aggressive_prediction_main$zi_age) / (1+exp(aggressive_prediction_main$zi_age))
aggressive_prediction_main$pcount_age <- exp(aggressive_prediction_main$count_age) * (1-aggressive_prediction_main$pzero_age)

#calculate differences
##zi
###age
age9to12_aggressive_pzero <- ((aggressive_prediction_main[2,5] - aggressive_prediction_main[1,5]) / aggressive_prediction_main[1,5]) * 100
round(age9to12_aggressive_pzero)
#106% increase
##count
age9to12_aggressive_pcount <- ((aggressive_prediction_main[2,6] - aggressive_prediction_main[1,6]) / aggressive_prediction_main[1,6]) * 100
round(age9to12_aggressive_pcount)
#14% decrease

#Plot zi model
##age
aggressive_main.age_zi <-
  ggplot(aggressive_prediction_main, aes(x=factor(Ages), y=pzero_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Probability of Zero") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03, 0.04, 0.05), label=c("0%","1%","2%","3%","4%","5%"), limits=c(0,0.05)) +
  geom_label(label = "106% increase", x = 1.5, y = 0.035)

#plot count model
##age
aggressive_main.age_ct <-
  ggplot(aggressive_prediction_main, aes(x=factor(Ages), y=pcount_age, group=1)) +
  geom_point(stat='summary', fun=sum) +
  stat_summary(fun=sum, geom="line") +
  labs(title="Age Only Model", x="Age (years)", y="Predicted Score") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_discrete(breaks = c(0, 3),label = c("9", "12")) +
  scale_y_continuous(limits=c(0,5)) +
  geom_label(label = "14% decrease", x = 1.5, y = 3.3)
```

##Export above graphs
```{r}
#age
##zero-inflated models
###internal
ggsave(internal_main.age_zi,device="png",filename="Figures/Age_Only_Internal_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###external
ggsave(external_main.age_zi,device="png",filename="Figures/Age_Only_External_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###anxdep
ggsave(anxdep_main.age_zi,device="png",filename="Figures/Age_Only_anxdep_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###withdep
ggsave(withdep_main.age_zi,device="png",filename="Figures/Age_Only_withdep_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###attention
ggsave(attention_main.age_zi,device="png",filename="Figures/Age_Only_attention_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###rulebreak
ggsave(rulebreak_main.age_zi,device="png",filename="Figures/Age_Only_rulebreak_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")
###aggressive
ggsave(aggressive_main.age_zi,device="png",filename="Figures/Age_Only_aggressive_ZI_Figures_3.20.23.png",width=4,height=4, units = "in")

##count models
###external
ggsave(external_main.age_ct,device="png",filename="Figures/Age_Only_External_Count_Figures_3.20.23.png",width=4,height=4, units = "in")
###anxdep
ggsave(anxdep_main.age_ct,device="png",filename="Figures/Age_Only_anxdep_ct_Figures_3.20.23.png",width=4,height=4, units = "in")
###withdep
ggsave(withdep_main.age_ct,device="png",filename="Figures/Age_Only_withdep_ct_Figures_3.20.23.png",width=4,height=4, units = "in")
###attention
ggsave(attention_main.age_ct,device="png",filename="Figures/Age_Only_attention_ct_Figures_3.20.23.png",width=4,height=4, units = "in")
###rulebreak
ggsave(rulebreak_main.age_ct,device="png",filename="Figures/Age_Only_rulebreak_ct_Figures_3.20.23.png",width=4,height=4, units = "in")
###aggressive
ggsave(aggressive_main.age_ct,device="png",filename="Figures/Age_Only_aggressive_ct_Figures_3.20.23.png",width=4,height=4, units = "in")
```
