---
title: 'CBCL~PM2.5*Age+Covariates Models with Model Checking'
author: "Claire Campbell; prior data cleaning by Hedyeh Admadi"
date: "Version `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    fig_caption: yes
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_rype: console
  chunk_output_type: console
---

<style type="text/css">

body, td {
   font-size: 13px;
}
code.r{
  font-size: 11px;
}
pre {
  font-size: 11px
}
</style>


# R set up

Script not shown in the HTML file.

Note that the data cleaning and exploration for this analysis is in a separate file called 
"HEI-Aim2-Data-Cleaning-Exploration-0219-2021".


```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE)
#Clear existing data and graphics
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
graphics.off()
invisible(gc()) #free up memrory and report the memory usage.

# To create Pdf
library(knitr)

# Importing Data
library(haven)
library(readxl)

# Table specific
library(xtable)
library(kableExtra)

# Data Cleaning and plotting
library(tidyverse)
library(dplyr)
library(plyr)
library(ggplot2)
library(scales)

# ggplot common legend
library(ggpubr)

# Skewness library
library(e1071)

# Matrix operations
library(matrixStats)

# Mixed Models
library(lme4)
library(nlme)
library(lmerTest) # to get p-values for lmer
require (HLMdiag) # Model diagnostics

# Recoding for the whole data frame
library(naniar)

# To read the lables
library(Hmisc)

# to order the data
library(doBy)

# to re-code variables
library(rockchalk)

# for reshape
library(MASS)

# descriptive and more
library(psych)

# correlogram plot
library(corrplot)

# vif
library(car)

#glmer diagnostics
library("fitdistrplus")

#outlier analysis and R^2
library(performance)

# linearity plot of glmer
library(ggResidpanel)

# interaction plots 
library(sjPlot)

#interaction plots
library(emmeans)

# Creating stratified tables
library(arsenal)

#For zero-inflated negative binomial modeling/model checking
library(NBZIMM)
library(nlme)
library(philentropy)
```

# Importing the Clean Data
```{r}
HEI_Aim2_Long <- read.csv("HEI_Aim2_Long.csv")
HEI_Aim2_Wide <- read.csv("HEI_Aim2_Wide.csv")

HEI_Aim2_Long_1KidPerFamily <- read.csv("HEI_Aim2_Long_1KidPerFamily.csv")
dim(HEI_Aim2_Long)
dim(HEI_Aim2_Wide)
dim(HEI_Aim2_Long_1KidPerFamily)


names(HEI_Aim2_Long)
names(HEI_Aim2_Wide)
names(HEI_Aim2_Long_1KidPerFamily)


# Note we are keeping all families but choosing one kid per family
length(unique(HEI_Aim2_Long$rel_family_id))
length(unique(HEI_Aim2_Long$subjectid)) # matches number of rows of wide data :)

length(unique(HEI_Aim2_Long_1KidPerFamily$rel_family_id))
length(unique(HEI_Aim2_Long_1KidPerFamily$subjectid))
```

## Copy baseline variables to all timepoints for full df
```{r}
#rename so can use later
names(HEI_Aim2_Long)[names(HEI_Aim2_Long) == 'prnt.empl.bl'] <- 'prnt.empl.b'

#create dataset for table and comparison
baseline_vars <- subset(HEI_Aim2_Long, HEI_Aim2_Long$eventname=="Baseline", select = c("subjectid", "sex", "race_ethnicity", "high.educ", "neighb_phenx_avg_p", "overall.income.b", "prnt.empl.b"))

#rename variables
names(baseline_vars)[names(baseline_vars) == 'sex'] <- 'sex.bl'
names(baseline_vars)[names(baseline_vars) == 'race_ethnicity'] <- 'race_ethnicity.bl'
names(baseline_vars)[names(baseline_vars) == 'high.educ'] <- 'high.educ.bl'
names(baseline_vars)[names(baseline_vars) == 'neighb_phenx_avg_p'] <- 'neighb_phenx_avg_p.bl'
names(baseline_vars)[names(baseline_vars) == 'overall.income.b'] <- 'overall.income.bl'
names(baseline_vars)[names(baseline_vars) == 'prnt.empl.b'] <- 'prnt.empl.bl'

#add to initial df
HEI_Aim2_Long_2 <- merge(HEI_Aim2_Long, baseline_vars, by="subjectid")
```

## Descriptive Table before further Cleaning
```{r}
#factor eventname
HEI_Aim2_Long_2$eventname <- as.factor(HEI_Aim2_Long_2$eventname)
HEI_Aim2_Long_2$eventname <- relevel(HEI_Aim2_Long_2$eventname , ref="Baseline")

#create smaller df
df_prior <- subset(HEI_Aim2_Long_2,select=c("subjectid","abcd_site","eventname","interview_age","reshist_addr1_pm252016aa_bl","prnt.empl.bl","overall.income.bl","sex.bl","race_ethnicity.bl","high.educ.bl","neighb_phenx_avg_p.bl","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_anxdep_r","cbcl_scr_syn_withdep_r","cbcl_scr_syn_attention_r","cbcl_scr_syn_rulebreak_r","cbcl_scr_syn_aggressive_r","cbcl_scr_syn_totprob_r"))
#create table
des_table_prior <- tableby(eventname ~ ., data = df_prior[ , -which(names(df_prior) %in% c("subjectid"))], total=F) 
summary(des_table_prior, title = "Descriptive Statistics by Eventname Before Cleaning")
```

# Creating variables for modeling and tables

The following variables are time-invariant, will use baseline covariates since PM2.5 collected at baseline:
- reshist_addr1_pm252016aa_bl which is the Baseline PM2.5.
- reshist_addr1_no2_2016_aavg_bl which is the Baseline NO2.
- sex.bl
- race_ethnicity.bl
- high.educ.bl
- prnt.empl.bl 
- neighb_phenx_avg_p.bl
- overall.income.bl 


The following variables are time-varying:
- all CBCL outcomes
- interview_age


## Copy baseline variables to all timepoints for 1KidPerFamily
```{r}
#rename so can use later
names(HEI_Aim2_Long_1KidPerFamily)[names(HEI_Aim2_Long_1KidPerFamily) == 'prnt.empl.bl'] <- 'prnt.empl.b'

#create dataset for table and comparison
baseline_vars_1KidPerFamily <- subset(HEI_Aim2_Long_1KidPerFamily, HEI_Aim2_Long_1KidPerFamily$eventname=="Baseline", select = c("subjectid", "sex", "race_ethnicity", "high.educ", "neighb_phenx_avg_p", "overall.income.b"))

#rename variables
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'sex'] <- 'sex.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'race_ethnicity'] <- 'race_ethnicity.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'high.educ'] <- 'high.educ.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'neighb_phenx_avg_p'] <- 'neighb_phenx_avg_p.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'overall.income.b'] <- 'overall.income.bl'
names(baseline_vars_1KidPerFamily)[names(baseline_vars_1KidPerFamily) == 'prnt.empl.b'] <- 'prnt.empl.bl'

#add to initial df
HEI_Aim2_Long_1KidPerFamily_2 <- merge(HEI_Aim2_Long_1KidPerFamily, baseline_vars, by="subjectid")
```

## Clean 1KidPerFamily
```{r}
## Cleaning
#merge Asian into Other group b/c statistically Asian group is too small
tapply(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, 
       HEI_Aim2_Long_1KidPerFamily_2$eventname,table, useNA = "always")

HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl <- 
  ifelse(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl=="Asian","Other",
         HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl)

tapply(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, 
       HEI_Aim2_Long_1KidPerFamily_2$eventname,table, useNA = "always")

#reformat variables
HEI_Aim2_Long_1KidPerFamily_2$eventname <- 
  as.factor(HEI_Aim2_Long_1KidPerFamily_2$eventname)

HEI_Aim2_Long_1KidPerFamily_2$eventname <- 
  relevel(HEI_Aim2_Long_1KidPerFamily_2$eventname , ref="Baseline")

table(HEI_Aim2_Long_1KidPerFamily_2$eventname, useNA = "always")


HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_internal_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_internal_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_external_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_external_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_anxdep_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_anxdep_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_withdep_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_withdep_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_attention_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_attention_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_rulebreak_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_rulebreak_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_aggressive_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_aggressive_r)
HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_totprob_r <- as.numeric(HEI_Aim2_Long_1KidPerFamily_2$cbcl_scr_syn_totprob_r)
HEI_Aim2_Long_1KidPerFamily_2$abcd_site <- as.factor(HEI_Aim2_Long_1KidPerFamily_2$abcd_site)
HEI_Aim2_Long_1KidPerFamily_2$subjectid <- as.factor(HEI_Aim2_Long_1KidPerFamily_2$subjectid)
HEI_Aim2_Long_1KidPerFamily_2$prnt.empl.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$prnt.empl.bl, levels = c("Employed", "Stay at Home Parent", "Unemployed", "Other"))
HEI_Aim2_Long_1KidPerFamily_2$overall.income.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$overall.income.bl, levels = c("[>=100K]", "[>=50K & <100K]", "[<50k]", "[Don't Know or Refuse]"))
HEI_Aim2_Long_1KidPerFamily_2$sex.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$sex.bl, levels = c("Male", "Female"))
HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$race_ethnicity.bl, levels = c("White", "Hispanic", "Black", "Other"))
HEI_Aim2_Long_1KidPerFamily_2$high.educ.bl <- factor(HEI_Aim2_Long_1KidPerFamily_2$high.educ.bl, levels = c("Post Graduate Degree", "Bachelor", "Some College", "HS Diploma/GED", "< HS Diploma"))
```

## Create Final Dataset
```{r results='asis'}
#create smaller df
df <- subset(HEI_Aim2_Long_1KidPerFamily_2,select=c("subjectid","abcd_site","eventname","interview_age","reshist_addr1_pm252016aa_bl","reshist_addr1_no2_2016_aavg_bl","prnt.empl.bl","overall.income.bl","sex.bl","race_ethnicity.bl","high.educ.bl","neighb_phenx_avg_p.bl","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_anxdep_r","cbcl_scr_syn_withdep_r","cbcl_scr_syn_attention_r","cbcl_scr_syn_rulebreak_r","cbcl_scr_syn_aggressive_r","cbcl_scr_syn_totprob_r"))

#complete cases because needed for zinb
df_cc <- df[complete.cases(df),]

#percentage of subjects lost with complete.cases
lost_sub <- data.frame(table(df$eventname))
colnames(lost_sub) <- c("eventname","abcd")
interim <- data.frame(table(df_cc$eventname))[2]
lost_sub$sample <- interim$Freq
lost_sub$diff <- lost_sub$abcd - lost_sub$sample
lost_sub$percent <- lost_sub$diff/lost_sub$abcd

#center age at 9years-old (i.e., 108 months)
df_cc$interview_age.c9 <- df_cc$interview_age-108
#change to years
df_cc$interview_age.c9.y <- df_cc$interview_age.c9/12
#center pm2.5 to 5 (recommended by WHO)
df_cc$reshist_addr1_pm252016aa_bl.c5 <- df_cc$reshist_addr1_pm252016aa_bl-5
#center no2 to 5.33 (recommended by WHO)
df_cc$reshist_addr1_no2_2016_aavg_bl.c533 <- df_cc$reshist_addr1_no2_2016_aavg_bl-5.33

#center around mean
neighb_phenx_avg_p.bl.cm <- df_cc$neighb_phenx_avg_p.bl - mean(df_cc$neighb_phenx_avg_p.bl)

#create table
des_table <- tableby(eventname ~ ., data = df_cc[ , -which(names(df_cc) %in% c("subjectid"))], total=F) 
summary(des_table, title = "Descriptive Statistics by Eventname After Cleaning")

Final_DF_Descriptives <- summary(des_table, title = "Descriptive Statistics by Eventname After Cleaning")
#write.csv(Final_DF_Descriptives, "Descriptives_Final_Dataset.csv")
```


# Internalizing

## CBCL + AP Longitudinal Models
Zero-Inflated (ZI) Negative Binomial (NB): glmm.zinb in NBZIMM package.

CBCL only needs one nested random intercept since we eliminated the family nesting
by choosing one kid per family.

```{r}
internal_zinb_r <- glmm.zinb(cbcl_scr_syn_internal_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(internal_zinb_r)
summary(internal_zinb_r$zi.fit)
anova(internal_zinb_r)
VarCorr(internal_zinb_r)
```

## Assumption checking for ZINB Models

- Zero inflated negative binomial (zinb) regression already has overdispersion and excess zeros
and this is accounted for in the zinb modeling chosen, "The data distribution combines the 
negative binomial distribution and the logit distribution"

- Details on zinb can be found here: 
[link](https://ncss-wpengine.netdna-ssl.com/wp-content/themes/ncss/pdf/Procedures/NCSS/Zero-Inflated_Negative_Binomial_Regression.pdf)

For Model Checking we will follow the following pdf:
[link](https://ncss-wpengine.netdna-ssl.com/wp-content/themes/ncss/pdf/Procedures/NCSS/Zero-Inflated_Negative_Binomial_Regression.pdf)
This info is further detailed/published in books by Cameron and Trivedi (2013) and Hilbe (2014) and in Garay, Hashimoto, Ortega, and Lachos (2011).

They suggest using Pearson residuals.

```{r}
#Check outlier/residuals with this df
internal_res <- df_cc
internal_res$level1_resid.raw <- residuals(internal_zinb_r)
internal_res$level1_resid.pearson <- residuals(internal_zinb_r, type="pearson")
#Add predicted values (Yhat)
internal_res$cbcl_scr_syn_internal_r_predicted <- predict(internal_zinb_r,internal_res,type="response")
#Incidence
internal_res$incidence <- estimate.probability(internal_res$cbcl_scr_syn_internal_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(internal_res$level1_resid.pearson)
```

### Incidence vs. X's Plots
"These plots show each of the independent variables plotted against the incidence as measured by Y (CBCL Outcome). They
should be scanned for outliers and curvilinear patterns."
```{r}
#age
ggplot(internal_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(internal_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```

### Residuals vs Y (CBCL Outcome) Plot
"This plot shows the residuals versus the dependent variable. It can be used to spot outliers."
```{r}
plot(internal_res$level1_resid.pearson, internal_res$cbcl_scr_syn_internal_r)
```

### Residuals vs Yhat Plot
"This plot shows the residuals versus the predicted value (Yhat) of the dependent variable. It can show outliers."
```{r}
plot(internal_res$level1_resid.pearson, internal_res$cbcl_scr_syn_internal_r_predicted)
```

### Residuals vs Row Plot
"This plot shows the residuals versus the row numbers. It is used to quickly spot rows that have large residuals."
```{r}
plot(as.numeric(rownames(internal_res)),internal_res$level1_resid.pearson)
```

### Residuals vs X's Plots
"These plots show the residuals plotted against the independent variables. They are used to spot outliers. They are
also used to find curvilinear patterns that are not represented in the regression model."
```{r}
#age
ggplot(internal_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(internal_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```

For below models, view Internalizing above for notes.

# Externalizing

## CBCL + AP Longitudinal Models
```{r}
external_zinb_r <- glmm.zinb(cbcl_scr_syn_external_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(external_zinb_r)
summary(external_zinb_r$zi.fit)
anova(external_zinb_r)
VarCorr(external_zinb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
external_res <- df_cc
external_res$level1_resid.raw <- residuals(external_zinb_r)
external_res$level1_resid.pearson <- residuals(external_zinb_r, type="pearson")
#Add predicted values (Yhat)
external_res$cbcl_scr_syn_external_r_predicted <- predict(external_zinb_r,external_res,type="response")
#Incidence
external_res$incidence <- estimate.probability(external_res$cbcl_scr_syn_external_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(external_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(external_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(external_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(external_res$level1_resid.pearson, external_res$cbcl_scr_syn_external_r)
```
### Residuals vs Yhat Plot
```{r}
plot(external_res$level1_resid.pearson, external_res$cbcl_scr_syn_external_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(external_res)),external_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(external_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(external_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```

# Anxious/Depressed

## CBCL + AP Longitudinal Models
```{r}
anxdep_zinb_r <- glmm.zinb(cbcl_scr_syn_anxdep_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(anxdep_zinb_r)
summary(anxdep_zinb_r$zi.fit)
anova(anxdep_zinb_r)
```

```{r}
# r2_efron(anxdep_zinb_r)
# anxdep_zinb_r$logLik
# 
# r2_efron(anxdep_nb_r$lme)
# anxdep_nb_r$logLik
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
anxdep_res <- df_cc
anxdep_res$level1_resid.raw <- residuals(anxdep_zinb_r)
anxdep_res$level1_resid.pearson <- residuals(anxdep_zinb_r, type="pearson")
#Add predicted values (Yhat)
anxdep_res$cbcl_scr_syn_anxdep_r_predicted <- predict(anxdep_zinb_r,anxdep_res,type="response")
#Incidence
anxdep_res$incidence <- estimate.probability(anxdep_res$cbcl_scr_syn_anxdep_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(anxdep_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(anxdep_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(anxdep_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(anxdep_res$level1_resid.pearson, anxdep_res$cbcl_scr_syn_anxdep_r)
```
### Residuals vs Yhat Plot
```{r}
plot(anxdep_res$level1_resid.pearson, anxdep_res$cbcl_scr_syn_anxdep_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(anxdep_res)),anxdep_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(anxdep_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(anxdep_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```

# Withdrawn/Depressed

## CBCL + AP Longitudinal Models
```{r}
withdep_zinb_r <- glmm.zinb(cbcl_scr_syn_withdep_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(withdep_zinb_r)
summary(withdep_zinb_r$zi.fit)
anova(withdep_zinb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
withdep_res <- df_cc
withdep_res$level1_resid.raw <- residuals(withdep_zinb_r)
withdep_res$level1_resid.pearson <- residuals(withdep_zinb_r, type="pearson")
#Add predicted values (Yhat)
withdep_res$cbcl_scr_syn_withdep_r_predicted <- predict(withdep_zinb_r,withdep_res,type="response")
#Incidence
withdep_res$incidence <- estimate.probability(withdep_res$cbcl_scr_syn_withdep_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(withdep_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(withdep_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(withdep_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(withdep_res$level1_resid.pearson, withdep_res$cbcl_scr_syn_withdep_r)
```
### Residuals vs Yhat Plot
```{r}
plot(withdep_res$level1_resid.pearson, withdep_res$cbcl_scr_syn_withdep_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(withdep_res)),withdep_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(withdep_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(withdep_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```



# Attention

## CBCL + AP Longitudinal Models
```{r}
attention_zinb_r <- glmm.zinb(cbcl_scr_syn_attention_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(attention_zinb_r)
summary(attention_zinb_r$zi.fit)
anova(attention_zinb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
attention_res <- df_cc
attention_res$level1_resid.raw <- residuals(attention_zinb_r)
attention_res$level1_resid.pearson <- residuals(attention_zinb_r, type="pearson")
#Add predicted values (Yhat)
attention_res$cbcl_scr_syn_attention_r_predicted <- predict(attention_zinb_r,attention_res,type="response")
#Incidence
attention_res$incidence <- estimate.probability(attention_res$cbcl_scr_syn_attention_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(attention_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(attention_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(attention_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(attention_res$level1_resid.pearson, attention_res$cbcl_scr_syn_attention_r)
```
### Residuals vs Yhat Plot
```{r}
plot(attention_res$level1_resid.pearson, attention_res$cbcl_scr_syn_attention_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(attention_res)),attention_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(attention_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(attention_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```



# Rulebreak

## CBCL + AP Longitudinal Models
```{r}
rulebreak_zinb_r <- glmm.zinb(cbcl_scr_syn_rulebreak_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(rulebreak_zinb_r)
summary(rulebreak_zinb_r$zi.fit)
anova(rulebreak_zinb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
rulebreak_res <- df_cc
rulebreak_res$level1_resid.raw <- residuals(rulebreak_zinb_r)
rulebreak_res$level1_resid.pearson <- residuals(rulebreak_zinb_r, type="pearson")
#Add predicted values (Yhat)
rulebreak_res$cbcl_scr_syn_rulebreak_r_predicted <- predict(rulebreak_zinb_r,rulebreak_res,type="response")
#Incidence
rulebreak_res$incidence <- estimate.probability(rulebreak_res$cbcl_scr_syn_rulebreak_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(rulebreak_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(rulebreak_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(rulebreak_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(rulebreak_res$level1_resid.pearson, rulebreak_res$cbcl_scr_syn_rulebreak_r)
```
### Residuals vs Yhat Plot
```{r}
plot(rulebreak_res$level1_resid.pearson, rulebreak_res$cbcl_scr_syn_rulebreak_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(rulebreak_res)),rulebreak_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(rulebreak_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(rulebreak_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```



# Aggressive

## CBCL + AP Longitudinal Models
```{r}
aggressive_zinb_r <- glmm.zinb(cbcl_scr_syn_aggressive_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid,
              zi_fixed = ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, zi_random = ~1|abcd_site, data = df_cc)

summary(aggressive_zinb_r)
summary(aggressive_zinb_r$zi.fit)
anova(aggressive_zinb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
aggressive_res <- df_cc
aggressive_res$level1_resid.raw <- residuals(aggressive_zinb_r)
aggressive_res$level1_resid.pearson <- residuals(aggressive_zinb_r, type="pearson")
#Add predicted values (Yhat)
aggressive_res$cbcl_scr_syn_aggressive_r_predicted <- predict(aggressive_zinb_r,aggressive_res,type="response")
#Incidence
aggressive_res$incidence <- estimate.probability(aggressive_res$cbcl_scr_syn_aggressive_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using ZINB, so make sure to check below plots
hist(aggressive_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(aggressive_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(aggressive_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(aggressive_res$level1_resid.pearson, aggressive_res$cbcl_scr_syn_aggressive_r)
```
### Residuals vs Yhat Plot
```{r}
plot(aggressive_res$level1_resid.pearson, aggressive_res$cbcl_scr_syn_aggressive_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(aggressive_res)),aggressive_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(aggressive_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(aggressive_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```


# Total Problems

## CBCL + AP Longitudinal Models
Convergence Error with ZINB Model - thinking it's b/c total problems might not be heavily zero inflated
```{r}
hist(df_cc$cbcl_scr_syn_totprob_r)
hist(df_cc$cbcl_scr_syn_totprob_r[df_cc$eventname=="Baseline"])
hist(df_cc$cbcl_scr_syn_totprob_r[df_cc$eventname=="1-year"])
hist(df_cc$cbcl_scr_syn_totprob_r[df_cc$eventname=="2-year"])
```

```{r}
# totprob_zinb_r <- glmm.zinb(cbcl_scr_syn_totprob_r ~ reshist_addr1_pm252016aa_bl*interview_age + race_ethnicity.1 + high.educ_bl+ prnt.empl.alltp  + neighb_phenx_avg_p + overall.income.alltp + sex, random = ~1|abcd_site/subjectid, 
#               zi_fixed = ~ reshist_addr1_pm252016aa_bl*interview_age + race_ethnicity.1 + high.educ_bl+ prnt.empl.alltp  + neighb_phenx_avg_p + overall.income.alltp + sex, zi_random = ~1|abcd_site/subjectid, data = df_cc)
# 
# summary(totprob_zinb_r)
# summary(totprob_zinb_r$zi.fit)
# anova(totprob_zinb_r)

#Trying just normal negative binomial model due to distribution of outcome
totprob_nb_r <- glmm.nb(cbcl_scr_syn_totprob_r ~ reshist_addr1_pm252016aa_bl.c5*interview_age.c9.y + race_ethnicity.bl + high.educ.bl+ prnt.empl.bl  + neighb_phenx_avg_p.bl.cm + overall.income.bl + sex.bl + reshist_addr1_no2_2016_aavg_bl.c533, random = ~1|abcd_site/subjectid, data = df_cc)

summary(totprob_nb_r)
anova(totprob_nb_r)
```

## Assumption checking for ZINB Models
```{r}
#Check outlier/residuals with this df
totprob_res <- df_cc
totprob_res$level1_resid.raw <- residuals(totprob_nb_r)
totprob_res$level1_resid.pearson <- residuals(totprob_nb_r, type="pearson")
#Add predicted values (Yhat)
totprob_res$cbcl_scr_syn_totprob_r_predicted <- predict(totprob_nb_r,totprob_res,type="response")
#Incidence
totprob_res$incidence <- estimate.probability(totprob_res$cbcl_scr_syn_totprob_r, method="empirical")

#Plotting histogram of residuals, but may be skewed since using nb, so make sure to check below plots
hist(totprob_res$level1_resid.pearson)
```
### Incidence vs. X's Plots
```{r}
#age
ggplot(totprob_res,aes(incidence,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(totprob_res,aes(incidence,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
### Residuals vs Y (CBCL Outcome) Plot
```{r}
plot(totprob_res$level1_resid.pearson, totprob_res$cbcl_scr_syn_totprob_r)
```
### Residuals vs Yhat Plot
```{r}
plot(totprob_res$level1_resid.pearson, totprob_res$cbcl_scr_syn_totprob_r_predicted)
```
### Residuals vs Row Plot
```{r}
plot(as.numeric(rownames(totprob_res)),totprob_res$level1_resid.pearson)
```
### Residuals vs X's Plots
```{r}
#age
ggplot(totprob_res,aes(level1_resid.pearson,interview_age)) + geom_point(color = "black") + geom_smooth(method = "loess")
#pm2.5
ggplot(totprob_res,aes(level1_resid.pearson,reshist_addr1_pm252016aa_bl)) + geom_point(color = "black") + geom_smooth(method = "loess")
```
